Data Preparation

### 2019-01-10 Data Preparation.Rmd

>>>>

```{r}
booked <- filter(d_transcripts, d_transcripts$`Booking Status Description`=="Booked")%>%
  mutate(`Booking Status Description`= case_when(Grade<5.5~"Completed Unsuccessfully",
                                                 Grade>5.5~"Completed with Success"))

clean_transcripts <- d_transcripts %>% 
  left_join(booked, by= c("ID", "Code", "Year", "Period", "Grade", "Attempt", "Course concentration", "student_Concentration", "Capstone Year", "After Graduation"), suffix=c("-old", "-new"))%>%
  select(-`After Graduation`)%>%
  mutate(Pass= case_when(
    (`Booking Status Description-new`=="Completed with Success")~"Pass",
    (`Booking Status Description-new`=="Completed Unsuccessfully")~"Fail",
    (`Booking Status Description-old`=="Completed with Success")~"Pass",
    (`Booking Status Description-old`=="Completed Unsuccessfully")~"Fail",
    T~"error in clean_transcripts"
  )) %>%
  select(-`Booking Status Description-new`,-`Booking Status Description-old`,-"UCM_Year-new")
```
